---
title: "nba_player_similarity"
author: "Lucas Bishop"
date: "June 17, 2021"
output: html_document
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## NBA Data Science


### Load Libraries

Load all libraries that are needed for the analysis

```{r, include=FALSE, message=FALSE}
library(tidyverse)
library(rvest)
library(BBmisc)
library(ggrepel)
library(corrplot)
library(factoextra)
library(kableExtra)
```

### Set up Data and Scrape (some) of the data from Internet
```{r}
setwd("C:/Users/bisho/Documents/NBA player siMLarity/")
traditional <- read_csv("data/36minutes.csv") %>% select(-badcol)
advanced <- read_csv("data/advancedNBA.csv") %>% select(-badcol)
# extra pages for misc df have only qualified players, qualifications found here: https://basketball.realgm.com/info/glossary
extra1 <- read_html("https://basketball.realgm.com/nba/stats/2019/Misc_Stats/Qualified/dbl_dbl/All/desc/ 1") %>%
  html_table("table#table-7945.tablesaw.compact.tablesaw-stack", header = NA, fill = TRUE)
extra2 <- read_html("https://basketball.realgm.com/nba/stats/2019/Misc_Stats/Qualified/dbl_dbl/All/desc/ 2") %>%
  html_table("table#table-4389.tablesaw.compact.tablesaw-stack", header = NA, fill = TRUE)
extra3 <- read_html("https://basketball.realgm.com/nba/stats/2019/Misc_Stats/Qualified/dbl_dbl/All/desc/ 3") %>%
  html_table("table#table-9644.tablesaw.compact.tablesaw-stack", header = NA, fill = TRUE)

```

Further prepare the data: 
```{r}

# need to get rid of positions with dashes in them too
# get rid of the win share stats that are redundant in misc dataset
misc <- rbind(extra1[[3]], extra2[[3]], extra3[[3]]) %>% select(-'#', -"OWS", -"DWS", -"WS")
merged_stats <- inner_join(traditional, advanced) %>% select(-Rk)


## cleanup before misc merge

misc$Player=gsub(",", "", misc$Player, fixed = TRUE)

full_stats <- full_join(merged_stats, misc, by = 'Player') %>%
  unique() %>% select(-Team) %>% mutate(MPG = MP / G)
```

Originally I was going to clean up the foreign names within R but got fed up and cleaned in exel and then saved...

BUT! Now we have a full data frame with semi-cleaned data that we can add more columns to if we find more interesting stats.

Now we want to filter this merged data for only entries that we are interested in:

```{r}
full_stats_qual <- full_stats %>% drop_na()
#This leaves us with a data frame of players that have data entries in all 65 variables, or 'relevant' players
# now to subset this data for only looking at players that play significant minutes. I chose 25
cutoff <- 25.5
full_stats_qual <- subset(full_stats_qual, MPG >= cutoff)
```


Lets see what that looks like:
```{r, echo=FALSE}
# will not show up if the global options are set to a dark theme
full_stats_qual %>% knitr::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "hover"))

```


















